A Decision Procedure for (Co)datatypes in SMT Solvers

### 2016-02-09 sister/sister.tex
some work on intro

\begin{abstract}
Datatypes and codatatypes are useful to represent infinite and potentially
infinite data structures and processes. We describe a decision procedure that
combines reasoning about datatypes and codatatypes. The procedure has been
integrated in CVC4, a state-of-the-art SMT (satisfiability modulo theories)
solver, which can be used both as a general constraint solver and as an
automatic theorem prover. An evaluation based on problems generated from
interactive formal proofs developed using the Isabelle proof assistant
demonstrates the potential of the decision procedure.
\end{abstract}

@@

@@

%  * relation to AI
%   * among the earliest AI goals
%   * yet somewhat disconnected from mainstream AI
%     (with some exceptions, e.g. Urban ..., MaSh)
%
%  * followed by an intro to SMT and what it's used for \\
%  * followed to why theories are important (more efficient reasoning) \\
%  * followed to why (co)datatypes are important
%
%  * both for proving
%   * not finitely axiomatizable
%  * and for model finding
%   * Nunchaku

>>>>

\begin{abstract}
Datatypes and codatatypes are useful to represent infinite and potentially
infinite data structures and processes. We describe a decision procedure that
combines reasoning about datatypes and codatatypes. The procedure has been
integrated in CVC4, a state-of-the-art SMT (satisfiability modulo theories)
solver, which can be used both as a general constraint solver and as an
automatic theorem prover. An evaluation based on problems generated from
interactive formal proofs developed using the Isabelle proof assistant
demonstrates the potential of our decision procedure.
\end{abstract}

@@

Automatic theorem proving
* much focus on FOL
* two main approaches:
  superposition---e.g., E, SPASS, Vampire
  SMT (satisfiability modulo theory) solvers---e.g., CVC4, veriT, Yices, Z3
* SMT is also useful for model finding, or constraint solving: given some   
  constraints, find an assignment of its variables that satisfy them

* strength of the SMT approach is that it can compose different efficient
  decision procedures and other solvers for various theories---e.g., equality,
  linear arithmetic, and first-order quantifiers.
* the main scientific question is: which theories would be useful to
  applications, and which ones can be supported efficiently in SMT solvers?

@@

%  * followed by an intro to SMT and what it's used for \\
%  * followed to why theories are important (more efficient reasoning) \\
%  * followed to why (co)datatypes are important
%
%  * both for proving
%   * not finitely axiomatizable
%  * and for model finding
%   * Nunchaku
